Dark matter halo concentrations with a bayesian approach

### 2014-09-05 paper/article.tex
better explanation for the relative error

\begin{equation}
\xi=\frac{1}{N}\sum\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
\end{equation}

Where $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively and $N$ the number of haloes with a certain number of particles. Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).

>>>>

\begin{equation}
\xi(n)=\frac{1}{\left|{\cal{H}}_n\right|}\sum_{{\cal{H}}_n}\left|\frac{c_{org}-c_{obt}}{c_{org}}\right|
\end{equation}

Where ${\cal{H}}_n$ corresponds to the set of haloes with $n$ particles, $c_{org}$ and $c_{obt}$ are the original and obtained concentrations respectively for each halo in ${\cal{H}}_n$ and $\left|{\cal{H}}_n\right|$ the number of haloes in ${\cal{H}}_n$. Then we calculate $\xi$ for each number of particles (20, 200, 2000 and 20000).
